---
title: "Report"
output: pdf_document
---

```{r wrap-hook, echo=F}
hook_output = knit_hooks$get('output')
knit_hooks$set(output = function(x, options) {
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})
```

# Introduction

This is the report of the analysis performed with the R package MSstats on the web application MSstats-Shiny.
The analysis was performed with the following packages:

```{r, linewidth=100}
sessionInfo()
```

The original data was collected using a `r params$p1` acquisition.  
The summary of the analysed data is:

```{r echo=F, linewidth=100}
tryCatch({
  print(str(get_data()))
  print(summary(get_data()))
},error =  function(e){
  knit_exit()
})

tryCatch({
  preprocess_data()
},error =  function(e){
  knit_exit()
})

```

# Quality control

The data was preprocessed with the following parameters:

* Log transformation: log`r params$p2`
* Normalization method: `r params$p3`
* Global standards: `r params$p4` `r params$p5`
* Summarization method: TMP
* Removed runs with over 50% missing: `r params$p6`
* Censoring assumptions: `r params$p7`
* Cutoff value for censoring: `r params$p8`
* Max quantile for censored: `r params$p9`
* Model based imputation: `r params$p10`
* All features used: `r params$p11`
* Number of top features used: `r params$p12`

The summary of the preprocessed data is:

```{r echo=F, linewidth=100}
tryCatch({
  str(preprocess_data())
}, error = function(e){
  knit_exit()
})


```

Preprocessed data and summarised data can be downloaded from the Quality Control window (preprocessing tab).

Plots of preprocessed data can be downloaded in the Quality Control window (plot tab).

# Statistical model 

The comparisons have been defined as follows:

```{r, linewidth=100}
tryCatch({
  comp_list$dList
}, error = function(e){
  knit_exit()
})

```

Which result in the comparison matrix:

```{r, linewidth=100}
tryCatch({
  matrix_build()
}, error = function(e){
  knit_exit()
})

```

The total number of proteins that are differentially expressed in the comparisons at `r input$signif` significance is: `r nrow(SignificantProteins())`.

```{r, linewidth=100}
tryCatch({
  
  req(SignificantProteins())
  head(SignificantProteins(),20)
  
}, error = function(e){
  knit_exit()
}
)

```

Plots of results can be downloaded from the Statistical Model window, Data Comparison tab.

Model assumptions can be verified with QQ Plots and ResidualPlots, which can be downloaded from the Statistical Model window, Model Assumptions tab.



