---
title: "MSstatsShiny Launch Instructions"
author: "Devon Kohler (<kohler.d@northeastern.edu>)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MSstatsPTM LabelFree Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=8, 
  fig.height=8
)
```

This Vignette goes over how to launch the `MSstatsShiny` R shiny application. 

## Installation

To install this package, start R (version "4.0") and enter:

``` {r, eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("MSstatsShiny")
```

```{r, message=FALSE, warning=FALSE}
library(MSstatsShiny)
```

## 1. Launch Function

After installation, running the application is as simple as executing a single 
command.

```{r, eval = FALSE, message=FALSE, warning=FALSE}
launch_MSstatsShiny()
```

Once this command is executed, the application will automatically start up in a 
different window. You can still view any warnings or errors in the R console 
where you ran the function. This can be helpful when debugging.

## 2. Cloud Version

`MSstatsShiny` is also available on the cloud at \url{www.msstatsshiny.com}. Due
to RAM constraints, the cloud version of the application is limited to files 
under 250 MB. Any larger files should be processed in a local instance of the 
application.

